---
title: "SMI"
author: "Selim Ach"
date: "10/17/2020"
output: pdf_document
---

The objective of this report is to provie an example of a high frequency chart with the possibility to change the scale at which information are displayed (change frequency and time frame), but also add specific information on the chart itself.

```{r, warning =FALSE, message=FALSE, echo = FALSE}

# Librairies

library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(ggthemes)

# Importing file
data_smi <- read_csv("Data/data_smi.csv")

data_smi <- data_smi %>% 
  mutate (date = dmy(date)) %>% 
  arrange(date)

```

#### A lineplot (from January 1, 2015 to April 29, 2020) indicating the fluctuation of the SMI index.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

data_smi_extr_2015_2019 <- data_smi %>% 
  filter(date >= as.Date("2015-01-01") & date <= as.Date("2020-04-29"))

g1 <- ggplot(
  data = data_smi_extr_2015_2019,
  mapping = aes(x = date,
    y = price)
) +
  geom_line()+
  labs(title = "SIM Values",
       subtitle = "January 1, 2015 - April 29, 2020",
       x = "Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = FALSE))

g1


```


#### A lineplot with a red line indicating a threshold is added to the plot.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

g2 <- ggplot(data = data_smi_extr_2015_2019,mapping = aes(x = date,y = price)) +
  geom_line()+
  geom_hline(yintercept = 8900,colour = "red")+
  labs(title = "SIM Values",
       subtitle = "from January 1, 2019
       Intercept at CHF 8900",
       x="Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = FALSE))

g2

```

#### Another interesting feature is to add another chart to zoom or to show the general trend of the time series.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

library (patchwork)

data_smi_extr_2020 <- data_smi %>% 
  filter(date >= as.Date("2020-01-01") & date <= as.Date("2020-04-29"))

g3 <- ggplot(
  data = data_smi_extr_2020,
  mapping = aes(x = date,
    y = price)
) +
  geom_line()+
  labs(title = "SIM Values",
       subtitle = "Year 2020",
       x = "Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = FALSE))

g1_bis <- ggplot(
  data = data_smi_extr_2015_2019,
  mapping = aes(x = date,
    y = price)) +
  geom_line(color = "red")+
  labs(title = "from Jan 2015 to Apr 2020")+
  theme_economist()+
  theme(plot.title = element_text(size = 12,vjust = 1.5))+
  theme(axis.text.x = element_text(size = 5))+
  theme(axis.text.y = element_text(size = 5))+
  theme(axis.title.x = element_blank())+
  theme(axis.title.y = element_blank())+
  theme(plot.title = element_text(size = 10))+
  scale_y_continuous(labels=function(x) format(x, big.mark = ".", decimal.mark = ",", scientific = FALSE))

layout <- c(
  area(
    t = 2, 
    l = 0,
    b = 7,
    r = 9
  ),
  area(
    t = 0,
    l = 6,
    b = 2,
    r = 9
  )
)

g3 + g1_bis +
  plot_layout(design = layout)

```






