---
title: "cartography"
author: "Selim Ach"
date: "11/20/2020"
output: github_document
---

The objective is to plot on a map some features of the city of Geneva including bike paths and also main train station. This visualization can be complemented by other information if available, such as road traffic during the day.

### City of Geneva 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning =FALSE, message=FALSE, echo = FALSE}

library(readr)
library(tidyverse)
library(dplyr)
library(tidyverse)
library(sf)
library(osmdata)
library(patchwork)

```

```{r, warning =FALSE, message=FALSE, echo = FALSE}

sitg <- st_read("Data/SHP_CAD_BATIMENT_HORSOL_TOIT_SP/CAD_BATIMENT_HORSOL_TOIT_SP.shp")


# Train stations
geneva_station <- st_read("Data/SHP_AGGLO_GARES/AGGLO_GARES.shp")

# Bike paths
geneva_bike <- st_read("Data/SHP_OTC_AMENAG_2ROUES/OTC_AMENAG_2ROUES.shp")

#lake geneva
lakes <- opq(c(6.093979, 46.185654, 6.206932, 46.231885)) %>%
  add_osm_feature(key = "natural", value = "water") %>%
  osmdata_sf() %>%
  unname_osmdata_sf() %>%   
  purrr::pluck("osm_multipolygons") 

#river geneva
river <- opq(c(6.093979, 46.185654, 6.206932, 46.231885)) %>% 
add_osm_feature(key = 'waterway', value = 'river') %>%
osmdata_sf() %>%
purrr::pluck('osm_lines')


getbb("geneva") %>%
  opq() %>%
  add_osm_feature(
    key = "highway",
    value = c(
      "motorway", "primary",
      "secondary", "tertiary"
    )
  ) %>%
  osmdata_sf() %>%
  purrr::pluck("osm_lines") %>%
  ggplot() +
  geom_sf(data = sitg) + # sitg layer
  geom_sf(data = geneva_bike, color = "dark green", size = 1 ) + # bike path layer
  geom_sf(data = geneva_station, color = "red", size = 3) + # Station layer
  geom_sf(data = lakes, fill = "#3182bd", alpha = 0.3) + #lake layer
  geom_sf(data = river,  color = "#3182bd", size = 1) + #river layer
  coord_sf(
    xlim = c(6.10, 6.20),
    ylim = c(46.185, 46.231885),
    expand = FALSE
  )+
  labs(title = "City of Geneva with location of train stations and bike paths",
       subtite= " ")+
  theme_void()

```

***
### City of Nyon

The following example is the creation of a map of the city of Nyon, focusing on main roads and pedestrian streets.

```{r, warning =FALSE, message=FALSE, echo = FALSE}

# Ploting the city of Nyon and associated roads

# nyon_area <- opq(c(6.086254,46.344439,6.333446,46.441524))
# Ploting just for fun but strugling to find access to additional  layers


small_streets <- opq(c(6.2, 46.36, 6.26, 46.41)) %>%
  add_osm_feature(
    key = "highway",
    value = c(
      "residential", "living_street",
      "unclassified","footway")
  ) %>%
  osmdata_sf() %>%
  purrr::pluck("osm_lines")

# bigger streets
streets <- opq(c(6.2, 46.36, 6.26, 46.41)) %>%
  add_osm_feature(
    key = "highway",
    value = c(
      "motorway", "primary",
      "secondary", "tertiary"
    )
  ) %>%
  osmdata_sf() %>%
  purrr::pluck("osm_lines")

ggplot() + 
  geom_sf(data = streets, color = "#fdbb84") +
  geom_sf(data = small_streets, color = "#fee8c8")+ 
geom_sf(data = river, fill = "#3182bd", alpha = 0.3) +
    geom_sf(data = lakes, fill = "#3182bd", alpha = 0.3) + #lake layer
  coord_sf(
    xlim = c(6.2,6.26),   
    ylim = c(46.36,46.41),
    expand = FALSE) + 
  theme(plot.title = element_text(hjust = 0))+
  theme_void()

```

Adding an extra layer with the map background, focusing this time on residential areas only (using the ggmap functionality)

```{r, warning =FALSE, message=FALSE, echo = FALSE}

library(ggmap)

q <- getbb("nyon") %>%
opq() %>%
  add_osm_feature(
    key = "highway",
    value = c("living_street","residential")
    )

env <- osmdata_sf(q)

nyon_map <- get_map(getbb("Nyon"))

ggmap(nyon_map)+
  geom_sf(data = env$osm_points,
          inherit.aes = FALSE,
          colour = "#238443",
          fill = "#004529",
          alpha = .5,
          size = 2,
          shape = 21)+
  theme(plot.title = element_text(hjust = 1))+
  theme_void()


```

