---
title: "Restaurant"
author: "Selim Ach"
date: "10/5/2020"
output: pdf_document
 
---

Very often data are presented in tabular format and the challenge is to be able to process information in order to provide relevant insights. 

It is also sometimes useful to display all the data sample, for a first visual inspection (e.g. identify potential outliers) and take a decision on how to narrow the sample to the variables of interest.

Hereadfter is an example of how data can be presented to have a first glance at the information and another chart with an additional layer of information. 

***

```{r, warning =FALSE, message=FALSE, echo = FALSE}

library(readr)
library(ggplot2)
library(ggthemes)

food_data <- read_csv("Data/fast_food.csv")

head(food_data, 15)

ggplot(food_data, aes(x = restaurant, y = calories, colour = restaurant)) +
  geom_jitter(width = 0.2)+
  theme_economist()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1.1,vjust = 0.8))+
  theme(legend.position="none")+
  theme(plot.title = element_text(size = 12, face = "bold"),
    legend.title = element_blank(), 
    legend.text=element_blank())+
  labs(title = "Calories in Food Menus ",
    subtitle = "Fast food restaurants",
    x="Restaurant", y="Calories")+
  theme(plot.title = element_text(size = 14,vjust = 1.5))
```

This chart is an overview of the fast food restaurants and associated menus with an indication of their level of calories. 

```{r, warning =FALSE, message=FALSE, echo = FALSE}

library(tidyverse)

food_data_calories<- food_data %>% 
  arrange(-calories) %>% 
  head(15)

food_data %>%
  ggplot( aes(x=restaurant, y=calories, color=sodium)) + 
    geom_violin(aes(fill=sodium)) +
  geom_jitter(height = 0, width = 0.4)+
    xlab("class") +
  theme_economist()+
  theme(legend.position="top") +
    labs(title = "Calories in Food Menus ",
    subtitle = "Level of sodium in each menu",
    x="Restaurant", y="Calories")+
  theme(plot.title = element_text(hjust = 0,vjust = 1.5))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1.1,vjust = 0.8))+
  theme(legend.title = element_text(size = 12),legend.text = element_text(color = "red", size = 10))+
  theme(legend.position = c(0.8, 0.9),
          legend.direction = "horizontal")

```


In addition to the level of calories per menu, this chart allows also to display the level of sodium.

