---
title: "SMI"
author: "Selim Ach"
date: "10/17/2020"
output: github_document
---

The objective of this report is to provide an example of a high frequency charts with the possibility to change the scale at which information are displayed (change frequency and time frame), but also add specific information on the chart itself. These types of charts can be fully customized depending on the business needs. 

More to come soon with dynamic charts and dashboards.

***

```{r, warning =FALSE, message=FALSE, echo = FALSE}

# Librairies

library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
library(ggthemes)

# Importing file
data_smi <- read_csv("Data/data_smi.csv")

data_smi <- data_smi %>% 
  mutate (date = dmy(date)) %>% 
  arrange(date)

```

#### A lineplot (from January 1, 2015 to April 29, 2020) indicating the fluctuation of the SMI index.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

data_smi_extr_2015_2019 <- data_smi %>% 
  filter(date >= as.Date("2015-01-01") & date <= as.Date("2020-04-29"))

g1 <- ggplot(
  data = data_smi_extr_2015_2019,
  mapping = aes(x = date,
    y = price)
) +
  geom_line()+
  labs(title = "SIM Values",
       subtitle = "January 1, 2015 - April 29, 2020",
       x = "Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = "'", decimal.mark = ",", scientific = FALSE))

g1


```


#### A lineplot with a red line indicating a threshold is added to the plot.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

g2 <- ggplot(data = data_smi_extr_2015_2019,mapping = aes(x = date,y = price)) +
  geom_line()+
  geom_hline(yintercept = 8900,colour = "red")+
  labs(title = "SIM Values",
       subtitle = "from January 1, 2019
       Intercept at CHF 8900",
       x="Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = "'", decimal.mark = ",", scientific = FALSE))

g2

```

#### Another interesting feature is to add another chart to zoom or to show the general trend of the time series.
```{r, warning =FALSE, message=FALSE, echo = FALSE}

library (patchwork)

data_smi_extr_2020 <- data_smi %>% 
  filter(date >= as.Date("2020-01-01") & date <= as.Date("2020-04-29"))

g3 <- ggplot(
  data = data_smi_extr_2020,
  mapping = aes(x = date,
    y = price)
) +
  geom_line()+
  labs(title = "SIM Values",
       subtitle = "Year 2020",
       x = "Date",
       y = "Price (CHF)",
       caption = "SMI")+
  theme_economist()+
  theme(plot.title = element_text(size = 14,vjust = 1.5))+
  scale_y_continuous(labels=function(x) format(x, big.mark = "'", decimal.mark = ",", scientific = FALSE))

g1_bis <- ggplot(
  data = data_smi_extr_2015_2019,
  mapping = aes(x = date,
    y = price)) +
  geom_line(color = "red")+
  labs(title = "Since Jan 2015")+
  theme_economist()+
  theme(plot.title = element_text(size = 12,vjust = 1.5))+
  theme(axis.text.x = element_text(size = 5))+
  theme(axis.text.y = element_text(size = 5))+
  theme(axis.title.x = element_blank())+
  theme(axis.title.y = element_blank())+
  theme(plot.title = element_text(size = 10))+
  scale_y_continuous(labels=function(x) format(x, big.mark = "'", decimal.mark = ",", scientific = FALSE))

layout <- c(
  area(
    t = 2, 
    l = 0,
    b = 7,
    r = 9
  ),
  area(
    t = 0,
    l = 6,
    b = 2,
    r = 9
  )
)

g3 + g1_bis +
  plot_layout(design = layout)

```

***

An interesting feature is to animate the chart

```{r, warning =FALSE, message=FALSE, echo = FALSE}

library(gganimate)

anim <- g3 +
  transition_reveal(date)

anim


```


***

In the next chart, simple forecast models are implemented to predict the values of the SMI, taking into account pre-covid period. Three models are presented here. The first one is a naive prediction, which consist of using the last value of the time series to predict the future. The second model, drift, consist of drawing a line between the first and the last observation to extrapolate future values.  The last one is a (simplistic) model showing the mean of the time series. 

```{r, warning =FALSE, message=FALSE, echo = FALSE}

# Ref: Forecasting: Principles and Practice, 
# Rob J Hyndman and George Athanasopoulos 
# Monash University, Australia 
# Link: https://otexts.com/fpp3

library (fabletools)
library (feasts)
library(forecast)
library(tsibble)
library(janitor)
library(forecast)

data_smi2 <- data_smi %>%
  mutate(day = row_number()) %>%
  as_tsibble(index = day)

data_smi_pre_covid <- data_smi %>%
  filter (yearmonth(date) < yearmonth("2020-02-01")) %>% 
  mutate(day = row_number()) %>%
  as_tsibble(index = day)

data_smi2_fit <- data_smi_pre_covid %>%
  model(Mean = fable::MEAN(price),
        Naive = fable::NAIVE(price),
        Drift = fable::RW(price ~ drift()))

data_smi_fct <- data_smi2_fit %>%
  forecast(h=250)

anchor <- data_smi2 %>%
  filter(yearmonth(date) == yearmonth("2020-02-01"))

data_smi_fct %>%
  autoplot(data_smi2,level = NULL) +
  autolayer(data_smi_pre_covid, price, color = "blue") +
  autolayer(anchor, price) +
  ggtitle("Daily SMI and Projection")+
  xlab("Days") + ylab("Price in CHF") +
  guides(colour = guide_legend(title = "Forecast"))+
  scale_y_continuous(labels=function(x) format(x, big.mark = "'", decimal.mark = ",", scientific = FALSE))+
  theme(plot.title = element_text(size = 12,vjust = 1.5))+
  theme_economist()+
  theme(legend.position= "bottom")

```



